VIPE: Virtualized Intermittently-Powered Executor

### 2017-07-24 paper/paper.tex
WAR inconsistency section complete
relocate the figure tex code

%replace XXX with the submission number you are given from the ASPLOS submission site.
\newcommand{\asplossubmissionnumber}{XXX}

\usepackage[normalem]{ulem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm} % environment for the algorithm code (like figure and table)
\usepackage{algorithmicx} % write the pseudo code
\usepackage[noend]{algpseudocode} % layout of the pseudo code
\usepackage{tikz} % needed for: tikz pics
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{natbib}
%\usepackage{graphicx}
%\usepackage{subfigure}
%\usepackage[inline]{enumitem}

@@

		In this paper we are introducing VIPOS a runtime library the implement the Virtualed Intermittent Execution Model. VIPOS adapts two methods for data protection. One relies on a virtual buffer and the other uses the Direct Memory Access (DMA). VIPOS is able to approach the optimal tasks devision during the runtime. VIPOS reduces an application execution time by XX and the energy by XX.

@@

\begin{figure}[t]
    \centering
         \subfloat[The energy cost of FRAM/SRAM \textbf{writes} operations.]{\includegraphics[width=0.48\columnwidth]{figures/fram_write.eps} }
         \subfloat[The energy cost of FRAM/SRAM \textbf{read} operations.]{\includegraphics[width=0.48\columnwidth]{figures/fram_read.eps}}
    \caption{The energy cost of accessing volatile/non-volatile memory}
    \label{fig:framEnergy}
\end{figure}

@@

\section{VIPOS: Virtualized Intermittently Powered Runtime Environment}
VIPOS is runtime library that facilitates tasks navigation and preserves data/memory consistency of the IPDs. It is able, on-demand, to merge tasks to reduce the number of commits to the non-volatile memory.

@@

\subsection{VIPOS: The Virtualizing Engine}
\subsubsection{Power Interrupt Immune Scheduler}
It utilizes a persistent circular buffer (persistent linked-list) to keep the state of a program across power failures. VIPOS provides an API to enable a programmer to have a full control over the execution flow of the program, i.e. (un)blocking a task or re-execute the same task which is particularly important in the intermittent execution to emulate a persistent loop.

@@

	\begin{algorithm}[t]
		\caption{Fixed virtual Task size}
		\label{algo:fixVirtTask}
		\scriptsize
		%\small
		\begin{algorithmic}[1]
			\State $VT \subset \text{\{VIPOS Tasks\}} $  \Comment{$VT:$ Virtual Task}
			\State VTS : VT size
			\State MVTS: maximum VT size
			\vspace{0.1cm}

@@

	\begin{algorithm}[t]
		\caption{Opportunistic virtual Task size}
		\label{algo:fixVirtTask}
		\scriptsize
		%\small
		\begin{algorithmic}[1]
			\State $VT \subset \text{\{VIPOS Tasks\}} $  \Comment{$VT:$ Virtual Task}
			\State VTS : VT size
			\vspace{0.1cm}

@@

VIPOS is able to virtually merge tasks to construct a bigger virtual task and commit the state of the virtual task instead of the individual real tasks. 
Fig.~\ref{fig:virtualTaskSize} show the benefit of virtualizing the Modular Intermittent Execution Mode (MIEM) in the best case scenario (continuous power supply).

@@

\section{Results}
We compare the performance of VIPOS against a state-of-the-art intermittent execution approach. For this purpose, we used two different applications: (i) A data decompression application, which utilizes Huffman decoding technique to decompress 100 byte of data.; (ii) A discrete Fourier transform (DFT) application that uses two different resolution (4 and 8 bites) to analyze a randomly generated signal.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.8\columnwidth]{figures/ipos_chain}
	\caption{Time to complation of VIPOS versus Chain. Decomp: Data decompression application. DFTx: Discrete Fourier Transform.}
	\label{fig:IPOSPerformance}
\end{figure}

Fig.~\ref{fig:IPOSPerformance} shows that VIPOS requires a shorter execution time to execute an application under the MIEM. The size of the virtual task that VIPOS uses equals One real task, in other words, no visualization is applied.

>>>>

%replace XXX with the submission number you are given from the ASPLOS submission site.
\newcommand{\asplossubmissionnumber}{39}

\usepackage[normalem]{ulem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm} % environment for the algorithm code (like figure and table)
\usepackage{algorithmicx} % write the pseudo code
\usepackage[noend]{algpseudocode} % layout of the pseudo code
\usepackage{tikz} % needed for: tikz pics
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{natbib}
\usepackage{tikz}
\usepackage{listings}

%\usepackage{graphicx}
%\usepackage{subfigure}
%\usepackage[inline]{enumitem}

@@

		In this paper we are introducing \sys a runtime library the implement the Virtualed Intermittent Execution Model. \sys adapts two methods for data protection. One relies on a virtual buffer and the other uses the Direct Memory Access (DMA). \sys is able to approach the optimal tasks devision during the runtime. \sys reduces an application execution time by XX and the energy by XX.

@@

\begin{figure}[t]
    \centering
         \subfloat[The energy cost of FRAM/SRAM \textbf{writes} operations.]{\includegraphics[width=0.48\columnwidth]{figures/fram_write.eps} }\\
         \subfloat[The energy cost of FRAM/SRAM \textbf{read} operations.]{\includegraphics[width=0.48\columnwidth]{figures/fram_read.eps}}
    \caption{The energy cost of accessing volatile/non-volatile memory}
    \label{fig:framEnergy}
\end{figure}

@@

\section{\sysfull}
\sys is runtime library that facilitates tasks navigation and preserves data/memory consistency of the IPDs. It is able, on-demand, to merge tasks to reduce the number of commits to the non-volatile memory.

@@

\subsection{\sys: The Virtualizing Engine}
\subsubsection{Power Interrupt Immune Scheduler}
It utilizes a persistent circular buffer (persistent linked-list) to keep the state of a program across power failures. \sys provides an API to enable a programmer to have a full control over the execution flow of the program, i.e. (un)blocking a task or re-execute the same task which is particularly important in the intermittent execution to emulate a persistent loop.

@@

	\begin{algorithm}[t]
		\caption{Fixed virtual Task size}
		\label{algo:fixVirtTask}
		\scriptsize
		%\small
		\begin{algorithmic}[1]
			\State $VT \subset \text{\{\sys Tasks\}} $  \Comment{$VT:$ Virtual Task}
			\State VTS : VT size
			\State MVTS: maximum VT size
			\vspace{0.1cm}

@@

	\begin{algorithm}[t]
		\caption{Opportunistic virtual Task size}
		\label{algo:fixVirtTask}
		\scriptsize
		%\small
		\begin{algorithmic}[1]
			\State $VT \subset \text{\{\sys Tasks\}} $  \Comment{$VT:$ Virtual Task}
			\State VTS : VT size
			\vspace{0.1cm}

@@

\sys is able to virtually merge tasks to construct a bigger virtual task and commit the state of the virtual task instead of the individual real tasks. 
Fig.~\ref{fig:virtualTaskSize} show the benefit of virtualizing the Modular Intermittent Execution Mode (MIEM) in the best case scenario (continuous power supply).

@@

\section{Results}
We compare the performance of \sys against a state-of-the-art intermittent execution approach. For this purpose, we used two different applications: (i) A data decompression application, which utilizes Huffman decoding technique to decompress 100 byte of data.; (ii) A discrete Fourier transform (DFT) application that uses two different resolution (4 and 8 bites) to analyze a randomly generated signal.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.8\columnwidth]{figures/chain_vipe}
	\caption{Time to complation of \sys versus Chain. Decomp: Data decompression application. DFTx: Discrete Fourier Transform.}
	\label{fig:IPOSPerformance}
\end{figure}

Fig.~\ref{fig:IPOSPerformance} shows that \sys requires a shorter execution time to execute an application under the MIEM. The size of the virtual task that \sys uses equals One real task, in other words, no visualization is applied.
